Molecular Gas Dynamics of the lensed wet-merger RXSJ1131-1123 at $z$=0.654

### 2016-05-17 WRITEUP/ms.tex
Co32 emission section done

% Done: PdBI observations, VLA observations, CARMA obs, HST astrometry, CO21 results, origin of \bco
%
%
%
%
%
\documentclass[]{emulateapj}
\usepackage{amsmath}
\input{preamble}
\slugcomment{To be submitted to the ApJ}

@@

%--------------------------------------------------------------------------
%                                Results
%--------------------------------------------------------------------------
\section{Results}
\subsection{\bco emission} %DONE
We dynamically resolved the \bco line emission toward the background galaxies
at $\gtrsim$27$\sigma$ significance, confirming the redshift at $z_{\rm CO}$ =
0.65370 $\pm$ 0.0005. A highly asymmetric double-horned line profile is
detected as shown in \Fig{CO21spec}. Fitting a double Gaussian results in peak
flux densities of 75.3$\pm$2.6 and 24.0$\pm$2.0 mJy, and a FWHM of
179$\pm$9 \kms and 255$\pm$28 \kms, respectively. The peaks are separated by
$\Delta v_{\rm sep}$ = 220 \kms. The integrated line flux is 24.1\,$\pm$\,2.3 Jy \kms. % see 15May16/

@@

\subsection{\bco kinematics} % DONE
A clear velocity gradient and an unusually high
velocity dispersion ($\gtrsim$400\kms) near the central region
is seen in \Fig{CO21highO}. While beam smearing is inevitably the
dominant factor in the observed velocity dispersion
at the spatial resolution of this data, the exceedingly
high velocity dispersion hints
at potential perturbations from the AGN, or internal turbulence due to
interactions with the companion, and/or instability due to the large gas
content. A velocity gradient across the source plane in \Fig{model} is also
found in our lens model. This further supports the idea of a kinematically-
ordered galaxy, but its emission has been lensed differentially.
In this scenario, RXJ1131 is a disrupted disk galaxy hosting an optically
bright quasar and is in the process of merging.
We will defer the discussion of the implications to \Sec{dynamics},
where we analyze the dynamics of the system in the source plane.

@@

\subsection{\cco emission}
\subsection{Interferometric Continuum}
2mm: resolved along the major axis, but unresolved along the minor axis. We decomposed the continuum from the foreground and background sources by subtracting a point
source model in the $uv-$plane (see Riechers+13 SMMJ04135 description)

>>>>

% Done: PdBI observations, VLA observations, CARMA obs, HST astrometry, CO21 results, origin of co21, co32 emission
%
%
%
%
%
\documentclass[]{emulateapj}
\usepackage{amsmath}
\input{preamble}
\slugcomment{To be submitted to the ApJ}

@@

%--------------------------------------------------------------------------
%                                Results
%--------------------------------------------------------------------------
\section{Results}
\subsection{\bco Emission} %DONE
We dynamically resolved the \bco line emission toward the background galaxies
at $\gtrsim$27$\sigma$ significance, confirming the redshift at $z_{\rm CO}$ =
0.65370 $\pm$ 0.0005. A highly asymmetric double-horned line profile is
detected as shown in \Fig{CO21spec}. Fitting a double Gaussian results in peak
flux densities of 75.3$\pm$2.6 and 24.0$\pm$2.0 mJy, and a FWHM of
179$\pm$9 \kms and 255$\pm$28 \kms, respectively. The peaks are separated by
$\Delta v_{\rm sep}$ = 220 \kms. The integrated line flux is 24.1\,$\pm$\,2.3 Jy \kms. % see 15May16/

@@

\subsection{\bco Kinematics} % DONE
A clear velocity gradient and an unusually high
velocity dispersion ($\gtrsim$400\kms) near the central region
is seen in \Fig{CO21highO}. While beam smearing is inevitably the
dominant factor in the observed velocity dispersion
at the spatial resolution of this data, the exceedingly
high velocity dispersion hints
at potential perturbations from the AGN, or internal turbulence due to
interactions with the companion, and/or instability due to the large gas
content. A velocity gradient across the source plane in \Fig{model} is also
found in our lens model. This further supports the idea of a kinematically-
ordered galaxy, but its emission has been lensed differentially.
In this scenario, RXJ1131 is a disrupted disk galaxy hosting an optically
bright quasar and is in the process of merging.
We will defer the discussion of the implications to \Sec{dynamics},
where we analyze the dynamics of the system in the source plane.

@@

\subsection{\cco Emission} % done
We detect resolved \cco line emission toward RXJ1131. The spectrum is shown in
\Fig{co32spec}, which seems to have a double-peak profile.
This is expected if RXJ1131 is truly a disk galaxy (see previous
sections). The high phase noise in the calibration leads to a low SNR
detection. We thus estimate the line intensity to be
35.7$\pm$ 21.9 Jy\,\kms by summing up fluxes over the
linewidth used to infer \bco line intensity ($\sim$700 \kms).

\begin{figure}[!Htbp]
\centering
\includegraphics[width=0.5\textwidth]{../Figures/coOverlay.eps}
\caption{
\carma \cco line profile (solid) without continuum subtraction is
over-plotted on the continuum-subtracted \bco line profile (dashed).
The velocity scale is with respect to $z$=0.6537, which corresponds to the dynamical center of the \bco line. The spectral resolution for \cco and \bco is 35.8 \kms and 21.5 \kms, respectively.
 \label{fig:co32spec}}
\end{figure}

\subsection{Interferometric Continuum}

At the position of \cco, continuum emission is not detected in
the line-free channels down to a 3$\sigma$ limit of 2.49mJy beam\pmOne.
This is consistent with the spectrum shown in \Fig{co32spec}.
The continuum is buried within the sensitivity limit of this data.
% (consistent with the Gaussian + poly fit to the spectrum continuum level: 2.2 $\pm$ 3.0 mJy).
% line free channels:1, 118, 160, 600
% nchan =(117+600-160+1) = 558
% sigma =  0.83 mJy/B

2mm: resolved along the major axis, but unresolved along the minor axis. We decomposed the continuum from the foreground and background sources by subtracting a point
source model in the $uv-$plane (see Riechers+13 SMMJ04135 description)
